Approximation as Differentiation

### 2025-05-24 main/introduction.tex
siskind08.

  In a simple query like this, it is easy to work out the dependency relationship between the input and output. However, the benefit of \GPS is that it is {\em automatic} for all programs, no matter how complex the relationship between input and output. Moreover, by changing what we mean by ``approximation'' we can compute a range of different information about a program.
\end{example}

>>>>

  In a simple query like this, it is easy to work out the dependency relationship between the input and output. However, the benefit of \GPS, and other program analysis-based techniques, is that it is {\em automatic} for all programs, no matter how complex the relationship between input and output. Moreover, by changing what we mean by ``approximation'' we can compute a range of different information about a program.
\end{example}
